Kindly Bent to Free Us

### 2019-11-11 kindly/lang.tex
Bring back many of the figures.
3.2 Typing: Fixed typos.

\begin{figure*}[b]
  \centering
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure*}

@@

\affe uses of kinds and constrained types to indicate
linear and affine types.
% Before explaining the details of our type system, we
% give a quick presentation of the kinds and constraints.
A kind $k$ is either a kind variable, $\kvar$, or a constant.
Each constant is composed of a ``quality'' and a ``level''.
The quality describes the use pattern of the type. It can be
unrestricted $\kun$, affine $\kaff$, or linear $\klin$. The level  $n \in \Nat \cup \{\infty\}$
describes the nested regions in which the value can be used.
Level $0$ refers to the top-level scope outside any region; we often elide it
and write $\kaff$ for $\kaff_0$. Level
$\infty$ refers to an empty region that is infinitely nested.
For instance, the constraint $\Cleq{\kvar}{\kun_\infty}$ indicates that
$\kvar$ must be unrestricted, but can be local to a region.

Kinds form a lattice with an ordering that implements two principles
(see \cref{sdtyp:lattice}). First, unrestricted values may be used
where affine ones are expected and affine ones are less restricted
than linear one as reflected in \TirName{Lat-UA} and \TirName{Lat-AL}.
Second, values usable at level $n$ may be used at any more deeply
nested level $n'$ (where $n\le\infty$ for any $n$) as defined in the \TirName{Lat-X-Level} axioms.

@@

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure}[tp]
  \begin{minipage}{0.33\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.65\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
    \end{mathpar}
    \caption{The {\sc Borrow}, {\sc Abs} and {\sc Var} rules}
    \label{selectrules:borrow}
    \label{selectrules:binders}
  \end{minipage}
\end{figure}

@@

\subsubsection{Copying and Splitting}
\label{sdtyping:split}
\begin{figure}[tp]
  \centering
  \begin{minipage}{0.35\linewidth}
    \begin{mathpar}
      \ruleSDPair
    \end{mathpar}
    \caption{The {\sc Pair} rule}
    \label{sdtyp:pair}
  \end{minipage}\hfill
  \begin{minipage}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\vdash_e$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

@@

    \end{tabular}
    \caption{Splitting rules for bindings}
    \label{sdtyp:split}
  \end{minipage}
\end{figure}

>>>>

\begin{figure*}[!tb]
  \centering
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure*}

@@

\affe uses kinds and constrained types to indicate
linear and affine types.
% Before explaining the details of our type system, we
% give a quick presentation of the kinds and constraints.
A kind $k$ is either a kind variable, $\kvar$, or a constant.
Each constant is composed of a ``quality'' and a ``level''.
The quality describes the use pattern of the type. It can be
unrestricted $\kun$, affine $\kaff$, or linear $\klin$. The level  $n \in \Nat \cup \{\infty\}$
describes the nested regions in which the value can be used.
Level $0$ refers to the top-level scope outside any region; we often elide it
and write $\kaff$ for $\kaff_0$. Level
$\infty$ refers to an empty region that is infinitely nested.
For instance, the constraint $\Cleq{\kvar}{\kun_\infty}$ indicates that
$\kvar$ must be unrestricted, but can be local to a region.

Kinds form a lattice with an ordering that implements two principles
(see \cref{sdtyp:lattice}). First, unrestricted values may be used
where affine ones are expected and affine ones are less restricted
than linear ones as reflected in \TirName{Lat-UA} and \TirName{Lat-AL}.
Second, values usable at level $n$ may be used at any more deeply
nested level $n'$ (where $n\le\infty$ for any $n$) as defined in the \TirName{Lat-X-Level} axioms.

@@

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
    \end{mathpar}
    \caption{The {\sc Borrow}, {\sc Abs} and {\sc Var} rules}
    \label{selectrules:borrow}
    \label{selectrules:binders}
  \end{minipage}
\end{figure*}

@@

\subsubsection{Copying and Splitting}
\label{sdtyping:split}
\begin{figure*}[tp]
  \centering
  \begin{minipage}{0.35\linewidth}
    \begin{mathpar}
      \ruleSDPair
    \end{mathpar}
    \caption{The {\sc Pair} rule}
    \label{sdtyp:pair}
  \end{minipage}\hfill
  \begin{minipage}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\vdash_e$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

@@

    \end{tabular}
    \caption{Splitting rules for bindings}
    \label{sdtyp:split}
  \end{minipage}
\end{figure*}
